Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-24 Ch1_movement_rates/Ch1_Figures.Rmd
Working on figure 5

@@

The violin plot here is made with all the data, the jitter points are a random sample of 200

@@

```{r}
z.joint_weib <- joint_weib %>% 
  mutate(est.shape = scale(est.shape),
         est.scale = scale(est.scale),
         meanweib = scale(meanweib),
         varweib = scale(varweib))

z.joint_weib %>%
  group_by(model) %>%
  #sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_shape

z.joint_weib %>%
  group_by(model) %>%
  #sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Scale") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_scale

z.joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = meanweib)) +
  geom_violin() +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Mean") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_mean

z.joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = varweib)) +
  geom_violin() +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Variance") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_variance

```{r}
z.joint_weib %>% 
  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
  ggplot(., aes(x = name, y = value, color = model)) +
  geom_boxplot() +
  theme_bw()

@@

rbind(CIs.cp.shape, CIs.pp.shape, CIs.np.shape, CIs.cp.scale, CIs.pp.scale, CIs.np.scale) %>% 
  as.data.frame() %>% 
  rename(low = V1, mean = V2, high = V3) %>%
  tibble::rownames_to_column("model") %>% 
  mutate(param = stringr::str_sub(model, start = 8),
         model =stringr::str_sub(model, start = 5, end = 6),
         model = toupper(model),
         model = factor(model, levels = c("CP", "PP", "NP"))) -> CIdata

CIdata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Shape") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ShapeCI

@@

# The proportion of shape parameter values above the sampling distribution is 
prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)

```{r fig.width=10}
data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata

@@

## Figure Dispersal Kernels

```{r}
cp_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = "lightgray"))

pp_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = "lightgray"))

np_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = "lightgray"))

>>>>

z.joint_weib <- joint_weib %>% 
  mutate(est.shape = scale(est.shape),
         est.scale = scale(est.scale),
         meanweib = scale(meanweib),
         varweib = scale(varweib))

@@

fig.5col <- c("#68655a", "#ff814f", "#31aec5")

z.joint_weib %>% 
  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
  ggplot(., aes(x = name, y = value, color = model)) +
  geom_boxplot() +
  labs(x = "Parameter", y = "Z score") +
  scale_x_discrete(labels = c("est.scale" = "Scale", "est.shape"="Shape", "meanweib" = "Mean", "varweib"="Variance")) +
  scale_color_manual(values = fig.5col) +
  theme_bw() +
  guides(color = guide_legend(title = "Model")) -> zscoreplot

#plot_grid(meanweib, varweib, nrow = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)

@@

@@

rbind(CIs.cp.shape, CIs.pp.shape, CIs.np.shape, CIs.cp.scale, CIs.pp.scale, CIs.np.scale) %>% 
  as.data.frame() %>% 
  rename(low = V1, median = V2, high = V3) %>%
  tibble::rownames_to_column("model") %>% 
  mutate(param = stringr::str_sub(model, start = 8),
         model =stringr::str_sub(model, start = 5, end = 6),
         model = toupper(model),
         model = factor(model, levels = c("CP", "PP", "NP"))) -> CIdata

joint_weib %>% 
  group_by(., model) %>% 
  summarise(meanshape = mean(est.shape),
            meanscale = mean(est.scale)) %>% 
  pivot_longer(cols = starts_with("mean")) %>% 
  mutate(param = stringr::str_sub(name, start = 5),
         mean = value) %>% 
  dplyr::select(., -c(value, name)) %>% 
  left_join(., CIdata) -> CIdata

CIdata %>% 
  pivot_longer(., cols = c(median, mean, low, high)) %>% 
  filter(., param == "shape" & name != "median") %>% 
  pivot_wider(names_from = name) -> CIshape

CIdata %>% 
  pivot_longer(., cols = c(median, mean, low, high)) %>% 
  filter(., param == "scale" & name != "median") %>% 
  pivot_wider(names_from = name) -> CIscale

cp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))

pp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))

np_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> pp.dens

ggplot() +
  np_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> np.dens

plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)

```{r}
cp.dens +
  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> pp.tail

np.dens +
  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> np.tail

plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)

```{r}
cp.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> pp.tail

np.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> np.tail

plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
```

```{r}
# all density means

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  # Everything after this line is the confidence intervals
  #   stat_function(fun = dweibull, args = list(shape = CIshape$low[1], scale = CIscale$low[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[2], scale = CIscale$low[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[3], scale = CIscale$low[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  # lims(x = c(0, 1500), y = c(0, 0.006)) +
  #     stat_function(fun = dweibull, args = list(shape = CIshape$high[1], scale = CIscale$high[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[2], scale = CIscale$high[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[3], scale = CIscale$high[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  lims(x = c(0, 1500), y = c(0, 0.0062)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
#coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0002)) +
    NULL
```

```{r}
ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  lims(x = c(0, 1500), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0003))
```

```{r eval=FALSE}
CIdata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Shape") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ShapeCI

@@

# The proportion of shape parameter values above the sampling distribution is 
prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
```

```{r fig.width=10, eval = FALSE}
data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata

@@

Dispersal Kernels

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  cp_lines +
  pp_lines +
  np_lines +
  lims(x = c(0, 1250)) +
  theme_bw()

```{r}
cp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))

pp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))

np_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))
